Lifting CDCL to Relational Domains

### 2016-10-13 experiments.tex
abstract
experiment reference

\section{Experimental Results}\label{experiments}

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
inside 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP\'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All the benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  To enable precise 
analysis using Astr{\'e}e, all our benchmarks are manually instrumented with 
partition directive which provides external hint to guide the trace partitioning 
heuristics inside the tool.  Usually, such high-precision makes the analysis
very expensive, and is not needed for static analysis of the code.  Without trace 
partitioning, the analysis using Astr{\'e}e shows high degree of imprecision.

### 2016-10-13 paper.tex
experiment reference

\author{Rajdeep Mukherjee\inst{1}\hskip 1em  Peter Schrammel\inst{2}\hskip 1em  Daniel Kroening\inst{1}}

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a combination of
abstract interpretation and the well-known Conflict-Driven Clause Learning 
(CDCL) algorithm that is used in SAT solvers.  ACDCL alternates between a 
model search that performs overapproximate deduction with constraint 
propagation and a conflict analysis that performs under-approximate 
abduction with heuristic choice.  
%
ACDCL has been successfully used with non-relational abstract domains 
such as intervals to improve the performance of a floating-point 
decision procedure.  Whereas the propositional level algorithms used 
in SAT solvers can be rather easily lifted from the boolean lattice to 
other non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions and clause learning.
%
In this paper, we present the non-trivial adaptations of the model search and 
conflict analysis algorithms in ACDCL in order to enable the use of relational 
abstract domains.  We have implemented these algorithms inside the 2LS 
verification tool and instantiated our analysis over a template polyhedra 
domain.  We evaluate the performance of our analyzer in comparison with 
program verifiers that uses propositional-level solvers and a static 
analysis tool.  
%
Experimental evidence on a set of benchmarks drawn from bit-vector 
regression in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several bounds checking benchmarks 
shows significant reduction in the number of decisions and backjumping iterations 
along with stronger deductions and learned clauses aided by the richer abstract 
domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

@@

%===============================================================================
%\input{experiments}
%===============================================================================

>>>>

\author{Rajdeep Mukherjee\inst{1}\hskip 1em  Peter Schrammel\inst{2}\hskip 1em
Daniel Kroening\inst{1}\hskip 1em Tom Melham\inst{1}}

\institute{University of Oxford, UK \and University of Sussex, UK \\
\email{\{rajdeep.mukherjee,kroening,tom.melham\}@cs.ox.ac.uk},
\email{p.schrammel@sussex.ac.uk}}

@@

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a combination of
abstract interpretation and the well-known Conflict-Driven Clause Learning 
(CDCL) algorithm that is used in SAT solvers.  ACDCL alternates between a 
model search that performs overapproximate deduction with constraint 
propagation and a conflict analysis that performs under-approximate 
abduction with heuristic choice.  
%
ACDCL has been successfully used with non-relational abstract domains 
such as intervals to improve the performance of a floating-point 
decision procedure.  Whereas the propositional level algorithms used 
in SAT solvers can be rather easily lifted from the boolean lattice to 
other non-relational domains, lifting them to relational domains is 
challenging because of relational properties of deductions and learnt clauses.
%
In this paper, we present the non-trivial adaptations of the model search and 
conflict analysis algorithms in ACDCL in order to enable the use of relational 
abstract domains.  We have implemented these algorithms inside the 2LS 
verification tool and instantiated our analysis over a template polyhedra 
domain.  We evaluate the performance of our analyzer in comparison with 
program verifiers that uses propositional-level solvers and a static 
analysis tool.  
%
Experimental evidence on a set of benchmarks drawn from bit-vector 
regression in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several bounds checking benchmarks 
shows significant reduction in the number of decisions and backjumping iterations 
along with stronger deductions and learnt clauses aided by the richer abstract 
domains.
%
\end{abstract}
%===============================================================================
\input{introduction}
%===============================================================================

@@

%===============================================================================
\input{experiments}
%===============================================================================
